library(readr)
install.packages("here")
library(here)
library(readxl)

getwd()

## Step 1: Read in the dataset `ages.csv`.

```{r}
# Code to read in the ages.csv data goes here! 
read_csv("Ages_Data/ages.csv")


```

## Step 2: Read in the dataset `ages_tab.txt`

```{r}
# Code to read in the ages_tab.txt data goes here! 
read_delim("Ages_Data/ages_tab.txt", delim = "\t")

```

## Step 3: Read in the dataset `ages_mystery.txt`

```{r}
# Code to read in the ages_mystery.txt data goes here! 
read_delim("Ages_Data/ages_mystery.txt")

```

## Step 4: Read in the dataset `ages.xlsx`

```{r}
# Code to read in the ages.xlsx data goes here! 
read_excel("Ages_Data/ages.xlsx")

```

## Step 5: Both `read.csv` and `read.table` have an optional argument called `stringsAsFactors`. Figure out what this does. -- converts character to factors

## Step 6: Find a way to use `read_csv()` to read `ages.csv` with the variable "Name" as a factor and "Age" as a character.

```{r}
# Code to read in the ages.csv with "Name" as a factor and "Age" as a character goes here! 

read_csv("Ages_Data/ages.csv", col_types = f)


```

------------------------------------------------------------------------
